[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-24 analysis/paper.Rmd
functionized plot for dynamic plotting

# write a function

@@

```{r plots}
# Fig 3 reproduction
g <- ggplot(race_summary, aes(x = year, y = happy_avg, color = factor(race)))
g + geom_point(size = .6) +
  geom_line(stat = "smooth",
            method = "lm", 
            se = FALSE, 
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Average Happiness by Race Trend",
       x = "Year",
       y = "Mean Happiness",
       caption = "Figure 3") +
  scale_color_manual(values=c("blue", "forestgreen", "dodgerblue"),
                     name="Race",
                     breaks=c(1, 2, 3),
                     labels=c("White", "Black", "Other")) +
  coord_cartesian(ylim = c(1.9,2.5)) # setting this to match the study excludes the lm via the above methodology
```

>>>>

# Function to demonstrate that we can write a function.  In this case, this function creates a neat ggplot based on
  # input for the data, x and y axes, factor, title, and x and y labels
study_plotter <- function(plot_data, x_input, y_input, factor_input,
                          factor_title_input = factor_input,
                          factor_labs_input = NULL,
                          title_input = paste0("Plot of ", x_input, " by ", y_input), 
                          xlab_input = x_input, 
                          ylab_input = y_input,
                          caption_input = NULL,
                          ylim_input){

  # Evaluate the combination of the data and the x_input, y_input, and factor_input (allows for dynamic plotting)
  x_input_eval <- eval(parse(text = paste0(plot_data, "$", x_input)))
  y_input_eval <- eval(parse(text = paste0(plot_data, "$", y_input)))
  factor_input_eval <- eval(parse(text = paste0(plot_data, "$", factor_input)))

  # Set plot params
  g <- ggplot(eval(as.name(plot_data)), aes(x = x_input_eval, y = y_input_eval, color = factor(factor_input_eval)))

  # add plot elements and plot
  g + geom_point(size = .6) +
    geom_line(stat = "smooth",
              method = "lm", 
              se = FALSE, 
              alpha = 0.5) +
    theme_bw() +
    labs(title = title_input,
         x = xlab_input,
         y = ylab_input,
         caption = caption_input) +
    scale_color_manual(values=c("blue", "forestgreen", "dodgerblue"),
                       name=factor_title_input,
                       breaks=c(1, 2, 3),
                       labels=factor_labs_input) +
    coord_cartesian(ylim = ylim_input) # setting this to match the study excludes the lm via the above methodology
}

@@

```{r plots}
# Fig 3 reproduction

study_plotter(plot_data = "race_summary", 
              x_input = "year", 
              y_input = "happy_avg", 
              factor_input = "race",
              factor_title_input = "Race",
              factor_labs_input = c("White", "Black", "Other"),
              title_input = "Trend of Average Happiness in the US by Race",
              xlab_input = "Year",
              ylab_input = "Mean Happiness",
              caption_input = "Figure 3",
              ylim_input = c(1.9,2.5))
